Something something progress in light

### 2022-08-06 2_SSL_EES/article/article_main.tex
added figure

>>>>

\begin{figure*}
 \centering
 \includegraphics[height=17cm]{2_SSL_EES/article/figures/chip_architecture_overview.pdf}
 \caption{Historical evolution of light-emitting diode chip architectures. Rows from top to bottom: classical chip with lateral current spreading; Osram’s thin GaN flip-chip (vertical) architecture; flip-chip architecture; chip-scale package flip-chip architecture. Shown are side views of chips without packages, along a cutaway line best suited to the features of each architecture. The cutaway surface is indicated by a red arrow with an eye on the overlaid top view of each chip. Note that the dimensions are not to scale, and smaller features are greatly exaggerated for clarity. Years indicated correspond to the earliest identified patent priority date. Black frames around certain designs indicate chip designs not brought to large-scale production. Abbreviations: GaN – Gallium Nitride, ITO – Indium Tin Oxide, MQW – Multiple Quantum Well. Source: adapted and compiled from multiple patents and industry publications. See Supplementary Information, section…, for the full list of sources and references.}
 \label{fgr:chip_architecture_overview}
\end{figure*}
